---
title: "P8105_HW5_jao2195"
author: "Jennifer Osei"
date: "2023-11-15"
output: github_document
---

```{r, message=FALSE}
#Needed Libraries
library(tidyverse)
library(readr)
library(readxl)
library(dplyr)
```

### Problem 2
This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

#### Problem 2.1 Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

```{r, message=FALSE}
#Created a vector of all files needed from our directory using list.files() function.
study_files <- list.files("data", full.names = TRUE)

#To see the list of Study Files we have in our folder, printing stored variable above.
study_files

# Defining a function to read data from a file
read_my_csv <- function(file_path) {
  mydata <- read_csv(file_path)
  mydata <- mutate(mydata, treatment_group = str_remove(basename(file_path), "\\.csv")) #Remove .csv
  mydata <- separate(mydata, treatment_group, into = c("arm", "subject_id"), sep = "_") #creating 2 columns one for Subject Arm and the other for Subject ID from the filename. 
  return(mydata)
}
```

#### Problem 2.2 
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe.

```{r}
# Use purrr::map to iterate over file names and read data for each file.
list_of_datasets <- purrr::map(study_files, ~read_my_csv(.))

# Bind all the individual datasets into a single dataframe.

my_fully_combined_dataset <- bind_rows(list_of_datasets)
```

#### Problem 2.3
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
#Tidying completed within function in part 2.1 by:
# 1) Separating the file name into two columns using mutate : Subject ID and Arm 
# 2) Removing the .csv suffix from file name.
# 3) Weekly Observations are "tidy"; week all lowercase and in same syntax, week_1 to week_8, across the whole datafile. 
```

#### Problem 2.4
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}

```

